
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Summary}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}

%---------------------------------------------------------
Software Engineer with system design and leading experience, creator of pet projects, freelancer

I enjoy creating value with software. I believe a good engineer must be a part of the entire process of creating software, including high level concept work, detailed technical design, implementation, deployment and maintanence. I strive to increase my existing experience on all of these fronts.

I do not have any preference between languages, components (backend/frontend) or technologies. I enjoy solving problems no matter where they are. I am always open to learning new technologies that can bring value to the project and myself.

My experience mainly consists of but not limited to high level project design, technical concept design, setting up Kubernetes clusters with Terraform, creating backends using Kotlin (ktor), Typescript (NodeJS/Express), Python (Flask) and creating frontends using Javascript/Typescript (React).

I am open for freelance projects where I can design, create and support solutions. I like to work with start-ups.

\end{cvparagraph}